A Machine Learning Approach to MLB Catcher Framing

### 2021-12-10 Slides.Rmd
Commit

```{r cars, echo = FALSE, message = FALSE, cache=TRUE}
x=c(-0.95,0.95,0.95,-0.95,-0.95)
y=c(1.5,1.5,3.5,3.5,1.5)
sz=data.frame(x,y)
# Take some samples to explore
train = usable_data %>% slice(1000:150000) %>%
  mutate(strike = as.character(strike)) %>%
  select(-catcher_name)

@@

\tiny
```{r, echo=FALSE}
data_no_catchers <- usable_data[, -18]

train <- sample(1:nrow(data_no_catchers), nrow(data_no_catchers)/2)
test <- (-train)

log_reg_fit <- glm(strike ~ ., data=data_no_catchers[train, ], family='binomial')

pred <- predict.glm(log_reg_fit, type='response', newdata = data_no_catchers[test, ])
pred[pred >= 0.5] <- 'strike'
pred[pred < 0.5] <- 'ball'

```

```{r}
conf_mx <- table(pred=pred, true=data_no_catchers[test, ]$strike)
error <- (conf_mx[2] + conf_mx[3])/length(pred)

@@

```{r, cache=T}
x <- model.matrix(strike ~ ., data = data_no_catchers)[, -1]
y <- data_no_catchers$strike

>>>>

```{r, echo = FALSE, message = FALSE, cache=TRUE}
x=c(-0.95,0.95,0.95,-0.95,-0.95)
y=c(1.5,1.5,3.5,3.5,1.5)
sz=data.frame(x,y)
# Take some samples to explore
train = usable_data %>% slice(1000:150000) %>%
  mutate(strike = as.character(strike)) %>%
  select(-catcher_name)

@@

\tiny
```{r, echo=FALSE}
load("Model-Outputs/logistic-CM.Rda")
load("Model-Outputs/logistic-error.Rda")

@@

```{r, cache=T}
data_no_catchers <- usable_data[, -18]
x <- model.matrix(strike ~ ., data = data_no_catchers)[, -1]
y <- data_no_catchers$strike
